### 2025-08-29 getting-started.qmd
20250829 - clarify inner join

An inner join includes all rows that are in **both** `x` **and** `y`.
An inner join will return one row of `x` for each matching row of `y`, and can duplicate values of records on either side (left or right) if `x` and `y` have more than one matching record.
It returns columns from `x` and `y`.
Here is how to merge two data frames using an inner join (`dplyr::inner_join()`):

>>>>

An inner join includes only those rows in `x` that have a matching record in `y` (i.e., the record must be in both `x` and `y`).
An inner join will return that rows of `x` and `y` that have matching records, and can duplicate values of records on either side (left or right) if `x` and `y` have more than one matching record.
It returns columns from `x` and `y`.
Here is how to merge two data frames using an inner join (`dplyr::inner_join()`):
